%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% CV - Bernardo Lopes %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper,hidelinks]{altacv}

%Layout
\geometry{left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm,paperheight=50cm}

%Packages
\usepackage{paracol}
\usepackage{gensymb}

% Remove automatic hyphenation
\usepackage[none]{hyphenat}
\let\raggedright\relax

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

%Colors
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{GoldenEarth}{HTML}{E7D192}
\definecolor{VividPurple}{HTML}{3E0097}

\colorlet{name}{black}
\colorlet{tagline}{VividPurple}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{subheading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{black}
\colorlet{sub}{SlateGrey}
\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\newcommand{\cvsubevent}[4]{%
    \sbox0{{\textbf{\color{accent}#2}}}%
    \sbox1{{\small\color{sub}\makebox[0.26\linewidth][l]{\cvDateMarker~#3}}}%
    \noindent%
    \makebox[\linewidth][s]{%
        \usebox0%
        \hfill%
        \textcolor{sub!30}{\hdashrule[0.5ex]{\dimexpr\linewidth-\wd0-\wd1-2\intextsep\relax}{0.6pt}{0.5ex}}%
        \hfill%
        \usebox1%
    }%
  \medskip\normalsize
}

\newcommand{\cveventinv}[4]{%
  {\large\color{emphasis}#1}
  \smallskip\normalsize
  \ifstrequal{#2}{}{}{
  \textbf{\color{accent}#2}
  \smallskip}
  \ifstrequal{#4}{}{}{{\small\hfill\color{emphasis}\makebox[0.1\linewidth][l]{\faMapMarker~#4}}}%
  \ifstrequal{#3}{}{}{{\small\hfill\color{emphasis}\makebox[0.26\linewidth][l]{\faCalendar~#3}}}\par
  \medskip\normalsize
}

\newcommand{\cvproject}[3]{%
    \sbox0{{\textbf{\small\color{accent}{#1}}}}%
    \sbox1{{\small\color{emphasis}#3\hspace{0.5em}\makebox[0.33\linewidth][l]{#2}}}%
    \noindent%
    \makebox[\linewidth][s]{%
        \usebox0%
        \hfill%        \textcolor{sub!30}{\hdashrule[0.5ex]{\dimexpr\linewidth-\wd0-\wd1-2\intextsep\relax}{0.6pt}{0.5ex}}%
        \hfill%
        \usebox1%
    }%
  \medskip\normalsize
}

%

\begin{document}
\name{Bernardo Lopes}
\tagline{Full-Stack Developer focused on Backend and Infrastructure}
%\photo{2.5cm}{}
\personalinfo{%
 \location{Betim, Brazil}
\email{bernardo.lopes.software@gmail.com}
\homepage{}
\linkedin{bernardo-lopes-3500b92b6/}
\github{BernardoAPL}

}

\begin{fullwidth}
  \makecvheader
\end{fullwidth}


%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% About %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \cvsection{About}

  \small{I am a developer specializing in \textbf{Backend} and \textbf{Infrastructure}, strengthened by a focus on \textbf{Software} and \textbf{Software Management}. My passion is building robust platforms for \textbf{clients}, creating sustainable \textbf{infrastructure as code}, and architecting systems in a simple and straightforward way. My experience spans projects in \textbf{Java}, \textbf{React}, and \textbf{Frontend (HTML, CSS, JS)}, enabling me to build platforms that are not only reliable and easy to maintain but also pleasant to use.}


  %\textcolor{emphasis}{Certifications:}\smallskip
  %\cvachievement{\faTrophy}{Fantastic Achievement}{and some details about it}

  \switchcolumn

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \cvsection{Education}

  \cvevent{B.S.\ in Software Engineering}{PUC Minas - Cora\c{c}\~ao Eucar\'{\i}stico}{Jan 2024 -- Present}{}

  \begin{itemize}
    \setlength{\itemindent}{0em}
    \item   \small{Project Management}
    \item   \small{Software Production and Development}
  \end{itemize}
  \cvevent{Industrial Automation Technician}{SENAI Maria Madalena Nogueira}{2021 -- 2023}{Betim, MG}

\begin{itemize}
  \setlength{\itemindent}{0em}
  \item \small{Technical training focused on electronics, sensors, PLCs, and automated systems.}
  \item \small{Programming logic controllers (PLCs) and integrating industrial systems.}
  \item \small{Hands-on projects involving electrical circuits, pneumatics, robotics, and process automation.}
\end{itemize}


\end{paracol}

\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Skills}

\small{
  \textcolor{emphasis}{Languages: }
  \smallskip
  \cvtag{English B2}
  \cvtag{Spanish A2}
}


\small{
  \textcolor{emphasis}{Languages: }
  \smallskip
  \cvtag{Java}
  \cvtag{TypeScript}
  \cvtag{JavaScript}
  \cvtag{C++}
  \cvtag{HTML}
  \cvtag{CSS}
}

\smallskip

\small{
  \textcolor{emphasis}{Frameworks: }
  \smallskip
  \cvtag{React}
  \cvtag{Spring Boot}
}

\smallskip

\small{
  \textcolor{emphasis}{Infrastructure \& Automation: }
  \smallskip
  \cvtag{PostgreSQL}
  \cvtag{MySQL}
  \cvtag{Firebase}
  \cvtag{n8n}
}

\smallskip

\small{
  \textcolor{emphasis}{DevOps: }
  \smallskip
  \cvtag{Git}
  \cvtag{GitHub Actions}
}

\smallskip

\small{
  \textcolor{emphasis}{Tools: }
  \smallskip
  \cvtag{VS Code}
  \cvtag{IntelliJ}
  \cvtag{Figma}
}


\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}

\medskip

\cveventinv{Municipality of Betim}{Ombudsman Office -- Statistics}{March 2024 -- July 2025}{Betim, MG}

\cvsubevent{}{Projects and Deliverables}{}{}

\begin{itemize}
  \item \small{Developed advanced \textbf{Power BI} dashboards integrated with multiple data sources.}
  \item \small{Automated reporting by integrating \textbf{Excel} with various corporate spreadsheets.}
  \item \small{Performed modeling and statistical analysis to generate strategic reports for municipal leadership.}
  \item \small{Created analytical reports and automated calculations to support decision-making.}
\end{itemize}

\medskip

\cveventinv{Municipality of Betim}{Technology Intern}{August 2025 -- Present}{Betim, MG}

\cvsubevent{}{Responsibilities and Activities}{}{}

\begin{itemize}
  \item \small{Provided \textbf{technical support} to system users, ensuring stability and fast resolution of incidents.}
  \item \small{Developed and programmed \textbf{internal solutions} to fix recurring problems and optimize workflows.}
  \item \small{Supported maintenance and continuous improvement of the systems used by municipal departments.}
  \item \small{Collaborated with operational teams to automate tasks and reduce manual errors.}
\end{itemize}

\medskip


\medskip

\smallskip
%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Key Projects}

\cvproject{CarExpress}{\href{https://github.com/BernardoApl/CarExpress}{github.com/BernardoApl/CarExpress}}{\faGithub}
\begin{itemize}
  \item \small{Complete vehicle management system with registration, search, update, removal, distance calculation between cities, automatic backup, and restoration.}
  \item \small{Built as a CLI application in \textbf{C++}, using object-oriented programming, binary \texttt{.dat} files, exception handling, vectors, and structs.}
  \item \small{Technologies: C++, OOP, Binary files, CLI}
\end{itemize}

\medskip

\cvproject{Fishing Pond Management System}{\href{https://github.com/ICEI-PUC-Minas-PMGES-TI/pmg-es-2025-2-ti2-3740100-pesque-e-pague}{github.com/ICEI-PUC-Minas.../pesque-e-pague}}{\faGithub}
\begin{itemize}
  \item \small{Full platform for managing pay-to-fish venues, integrating inventory, sales, reservations, equipment rentals, and financial reports in a single system.}
  \item \small{Designed to replace manual processes, increase operational efficiency, and improve the customer experience.}
  \item \small{Technologies: TypeScript, React, Java, Spring Boot, PostgreSQL}
\end{itemize}

\medskip

\cvproject{Payroll Calculation}{\href{https://github.com/pm-puc-minas/calculo-folha-pagamento-lab-1-grupo-1}{github.com/pm-puc-minas/calculo-folha-pagamento}}{\faGithub}
\begin{itemize}
  \item \small{Payroll system that calculates salaries, bonuses, benefits, legal deductions (INSS, FGTS, IRRF), and generates a complete payroll report for users.}
  \item \small{Includes a frontend in \textbf{TypeScript + React} and a backend in \textbf{Java Spring Boot}, with unit tests and REST APIs for managing employees.}
  \item \small{Technologies: Java Spring Boot, React, TypeScript, CSS3, PostgreSQL}
\end{itemize}

\medskip


\end{document}
